---
title: "CorrDrugTumorMSI"
author: "Mridula Prasad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The **CorrDrugTumorMSI** package contains different functions to analyze untargeted drug Mass Spectrometry Imaging data. The main objective of package is to provide methods to link observed drug distribution with unsupervised clusters identified. 


## Preprocessing of MSI data

#PreprocessingMSIData

Function does preprocessing of MSI data available in analyze 7.5 format. The function first creates adaptive bins based on the peaks size in maximum intensity reference spectrum from given MSI data. Inside
created bins, peaks selection performed using local maxima search approach. Apart from peaks selection, there is an option to exclude high intensity peaks from the edge of the tissue and/or remove peaks with small coverage area. 

folderpath <- 'path of folder contains MSI data'\
mat       <- PreprocessingMSIData('folderpath')\


IonInensityMatrix   <- mat[[1]][[1]]  ## Ion intensity matrix  \
ycord               <- mat[[1]][[3]]  ## y-coordinate of MSI data \   
xcord               <- mat[[1]][[2]]  ## x-coordinate of MSI data \



## Clustering of input data matrix

```{r}
library(CorrDrugTumorMSI)
data('spdata')
par(mar=c(1, 1, 1, 1))

clusteredImg <- BisectKmeansClustering(spdata,cluster.size = 0.5)
dim(clusteredImg) <- c(80,10)
image(clusteredImg,axes=FALSE)

```

## Creates a spatial correlogram of spatial data 


```{r}

xycoord  <- as.matrix(expand.grid(1:80,1:10))
spcor <- CreateSpatialCorrelogram(xycoord,spdata[,1])

```


## Creates a LISA map

```{r}
par(mar=c(1, 1, 1, 1))
ionImg <- spdata[,1]
dim(ionImg) <- c(80,10)
LISAmap <- CreateLISAmap(ionImg,distthrs = 3)

```

## Quantitative analysis of LISA map 

```{r}
par(mar=c(1, 1, 1, 1))
Qlisa <- ClusteredLISAimgQA(clusteredImg,LISAmap)

```


